Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-11-30 dsn-2018/bare_conf.tex
Changes suggested by KMayo
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

Cryptographic hash functions form the core of many protocols. From file
integrity checks to verify long term storage of data, to cache invalidation
techniques, and use as a building block in network protocols such as Kerberos
and TLS, this class of functions necessarily has strong guarantees about
properties of its members. There are three basic properties hash
functions must have to be considered cryptographically secure:
\begin{itemize}
    \item \textbf{Preimage Resistance}: It should be computationally hard to find
        the inverse of a hash function.
    \item \textbf{Second Preimage Resistance}: Given an input block, it should be
        computationally hard to find a second block which hashes to the
        same value as the first block.
    \item \textbf{Collision Resistance}: It should be computationally hard to find two
        blocks which hash to the same value.
\end{itemize}
Note that a second preimage is necessarily a collision and is also a stronger
result in practice.

@@

From a cryptographic perspective, the existence of a feasible collision attack
breaks the requisite properties, thus deprecating the function's use. In some
instances however, there continues to be widespread use of deprecated hash
functions. One widespread example is the continued use by Git of SHA-1, despite
M. Stevens et al. publishing a full SHA-1 collision in February of 2017
\cite{cryptoeprint:2017:190}. However, this attack had a bound of $2^{63.1}$ --
faster than the theoretical $2^{80}$ but still requiring significant compute
resources.

We seek to address the problem of evaluating the use cases for a collision,
to determine--or partially determine--whether or not a collision affects
a particular system. This paper contributes several novel techniques to
logical cryptanalysis and uses these techniques to derive metrics of the
trustworthiness of hash functions. We claim the following results are novel
in the field:
\begin{itemize}
    \item We define the neighborhood of a class of collisions and show that
        it is frequently non-empty.
    \item We discuss techniques for finding useful collisions within a
        class of collisions.
    \item We propose additional techniques for building new classes of
        collisions and show that collisions in MD4 can be found inductively.
    \item We propose five universal metrics for evaluating the utility of
        a class of collisions.
\end{itemize}

>>>>

Cryptographic hash functions form the core of many protocols. With widespread
use as file integrity checks to verify long term storage of data, as cache
invalidation techniques, and as a building block in network protocols such as
Kerberos and TLS, this class of functions necessarily has strong guarantees
about properties of its members. There are three basic properties hash
functions must have to be considered cryptographically secure:
\begin{itemize}
    \item \textbf{Preimage Resistance}: It should be computationally hard to find
        the inverse of a hash function.
    \item \textbf{Second Preimage Resistance}: Given an input block, it should be
        computationally hard to find a second block which hashes to the
        same value as the first block.
    \item \textbf{Collision Resistance}: It should be computationally hard to find two
        blocks which hash to the same value.
\end{itemize}
Note that a second preimage is necessarily a collision and is also a stronger
result in practice.

@@

From a cryptographic perspective, the existence of a feasible collision attack
breaks the requisite properties, thus deprecating the function's use. In some
instances however, there continues to be widespread use of deprecated hash
functions. One widespread example is the continued use by Git of SHA-1, despite
M. Stevens et al. publishing a full SHA-1 collision in February of 2017
\cite{cryptoeprint:2017:190}. However, this attack had a bound of $2^{63.1}$ --
faster than the theoretical $2^{80}$ but still requiring significant compute
resources to find.

We seek to address the problem of evaluating the use cases for a collision,
to determine whether or not a collision affects a particular system. This
paper contributes several novel techniques to logical cryptanalysis and uses
these techniques to derive metrics of the trustworthiness of hash functions.
We claim the following results are novel in the field:
\begin{itemize}
    \item We define the neighborhood of a class of collisions and show that
        it is frequently non-empty.
    \item We discuss techniques for finding useful collisions within a
        class of collisions.
    \item We propose additional techniques for building new classes of
        collisions and show that collisions in MD4 can be found inductively.
    \item We propose five universal metrics for evaluating the utility of
        a class of collisions.
\end{itemize}
